---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  comment = ""
)
```

# boltr

<!-- badges: start -->
<!-- badges: end -->

This is an experimental calling Neo4J bolt protocol from R, via NodeJS. 

Note that you'll need  to have NodeJS installed to run this. 

Please do not use for now, this is still in an experimental phase.

## Install 

``` r
remotes::install_github("neo4r/boltr")
```

## Use

The first time you will use this package, you will need to install the Node infrastructure: 

```{r eval = FALSE}
boltr::boltr_npm_install()
```

Then, you can call NodeJS with:

```{r}
boltr::boltr_run(
  url = 'bolt://localhost:7687', 
  user = 'neo4j', 
  password = 'password', 
  cypher = 'MATCH (tom {name: "Tom Hanks"}) RETURN tom;'
)
```

The output is the raw, unparse JSON. 
You can turn it to an R list with `{jsonlite}`:

```{r}
library(magrittr)
boltr::boltr_run(
  url = 'bolt://localhost:7687', 
  user = 'neo4j', 
  password = 'password', 
  cypher = 'MATCH (tom {name: "Tom Hanks"}) RETURN tom;'
) %>% 
  jsonlite::fromJSON()
```

